\begin{abstract}
Existing event extraction systems are typically investigated in the supervised
learning paradigm. The effectiveness of these systems heavily relies on the quality of
expert-annotated datasets which still require a costly and time-consuming process to construct.
 As a result, the built datasets
often only cover a limited variety of event types, making the
learned event extractor hard to generalize. In this paper, we address the problem
of automatically building event extractors for rich event types with little expert involvement.
We achieve this by employing distant supervision to automatically create event annotations from
unlabelled data using structured knowledge bases. We then propose a novel
neural network model with ILP-based inference, committing to detecting events of various types and extracting
their corresponding arguments involved.
We evaluate our approach by automatically collecting training data for many event types from Freebase, where
our proposed extraction model is designed to identify both typed event mentions and typed arguments. Both automatic and
manual evaluations demonstrate that it is possible to learn to effectively extract
various events without human-annotated training data.

%
%and rely on expert-annotated datasets, with limited event types.
%%such as ACE and ERE event extraction frameworks.
%However, designing and constructing these
%high-quality corpora, usually with limited size and coverage of event types,  is costly, which
%makes learned extractors hard to generalize.  With the essence of distant supervision,
%%Inspired by some Freebase schemas which share similar structures with ACE event templates,
%we investigate the possibilities of automatic construction of training data for various event types
%with the help of structured knowledge bases.
%the following problems in this paper: can we generate a feasible dataset for event extraction with Freebase automatically and is it possible to extract events on this dataset.
%We first propose four hypotheses based on our observation and produce our dataset accordingly. Then,
%We further propose a novel neural network with ILP-based post inference, committing to
%handling two challenges in event extraction: multi-type events and multi-word arguments.
%Both automatic and manual evaluations demonstrate that it is possible to learn to extract various  events, according to existing knowledge bases, without human-annotated training data.
\end{abstract}
